---
title: "Assessment 1"
author: "zheng WANG S8069479"
date: "2023-03-09"
output: html_document
---

# RMarkdown editing
**R Markdown is a file format for making dynamic documents with R. An R Markdown document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code.**
**Some of the advantages of using R markdown include:**
*1.Explicitly links your data with your R code and output creating a fully reproducible workflow.*
*2.You can create a wide variety of output formats*
*3.Increases the efficiency of your workflow*

-[Rmarkdown](https://rmarkdown.rstudio.com/lesson-8.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
fastfood <- read_csv("fastfood_calories.csv")

```
# prints out the firsts 10 rows of the dataset

```{r kable}
library(readr)
library(knitr)
fastfood<- read_csv("fastfood_calories.csv")
head(fastfood,10,"simple")

```
# prints out the first 10 rows and the first 5 variables
```{r kable2}
library(readr)
library(knitr)
fastfood<- read_csv("fastfood_calories.csv")
knitr::kable(fastfood[1:10,1:5],align="lcccc")

```



