---
title: "Assessment1 part2"
author: "zheng WANG S8069479"
date: "2023-03-11"
output: html_document
---


# RMarkdown editing
**R Markdown is a file format for making dynamic documents with R. An R Markdown document is written in markdown (an easy-to-write plain text format) and contains chunks of embedded R code.**
**Some of the advantages of using R markdown include:**
*1.Explicitly links your data with your R code and output creating a fully reproducible workflow.*
*2.You can create a wide variety of output formats*
*3.Increases the efficiency of your workflow*

-[Rmarkdown](https://rmarkdown.rstudio.com/lesson-8.html)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
fastfood <- read_csv("fastfood_calories.csv")

```

# prints out the firsts 10 rows of the dataset
```{r kable}
library(readr)
library(knitr)
fastfood<- read_csv("fastfood_calories.csv")
head(fastfood,10,"simple")

```

# prints out the first 10 rows and the first 5 variables
```{r kable2}
library(readr)
library(knitr)
fastfood<- read_csv("fastfood_calories.csv")
knitr::kable(fastfood[1:10,1:5],align="lcccc")

```

## Part2
# Display the oberservations that has more than 1000 calories
```{r}
library(dplyr)
filter(fastfood, calories>1000) %>% 
  kable()
```

#Arrange observations with more than 40 in total_fat and more than 80 in total_carb in the descending order (PLEASE USE THE VARIABLE OF YOUR CHOICE TO ORGANISE THE DESCENDING ORDER) and save them to a new variable (dataset) called `dont_eat_this`
```{r}
dont_eat_this <-fastfood %>% filter(total_fat> 40 & total_carb> 80)
fastfood %>% filter(total_fat> 40 & total_carb> 80) %>% kable()
```

# Using the initial dataset variable, use `case_when()` to create a new variable `heavy_food` which is equal to "heavy" when total calories (`calories`) are greater than 500, "low" when total calories are less than 250 and "average" for all other cases. Count the number of observations in each created category.
```{r}
fastfood <- fastfood %>% mutate(heavy_food = case_when(calories > 500 ~ "heavy",calories < 250 ~ "low",TRUE ~ "average"))
fastfood %>% count(heavy_food)
```

#Display the types of variables in the dataset using `skimr` package
```{r}
library(skimr)
skim(fastfood)
```

#Present the count observations from each restaurant in a descending order
```{r}
fastfood %>%
  count(restaurant, wt = NULL, sort = TRUE, name = "res_num") %>% 
  kable()
```

#Show the number of distnct items on a menu in the dataset
```{r}
fastfood %>%
  arrange(desc(restaurant)) %>%
  kable()
n_distinct(fastfood)
```

#Using groupings (group_by()), summarise and display the average number of calories for each restaurant.
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(mean_calories = mean(calories, trim = 0, na.rm = FALSE)) %>% 
  ungroup() %>% 
  kable()
```

#Add variables to the dataset, which:- calculates the average calories per type of restaurant and call it `average_calories` - 
```{r}
average_calories <- fastfood %>%
  group_by(restaurant) %>%
  summarise(average_calories = mean(calories))%>%
  arrange(desc(average_calories)) %>%
  ungroup()

kable(average_calories)
```

#calculates the maximum total_fat per type of restaurant and call it `max_fat` - calculates the minimum cholesterol per type of restaurant and call it `min_cholesterol` 
```{r}
max_fat <- fastfood %>%
  group_by(restaurant) %>%
  summarise(max_fat = max(total_fat)) %>%
  arrange(desc(max_fat)) %>%
  ungroup() 
kable(max_fat)

min_cholestrol <- fastfood %>%
  group_by(restaurant) %>%
  summarise(min_cholestrol = min(cholesterol)) %>%
  arrange(desc(min_cholestrol)) %>%
  ungroup() 
kable(min_cholestrol)
```

#Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. 
```{r}
library(ggplot2)
variable_x = 'restaurant'
variable_y = 'total_fat' 
fastfood %>% 
  group_by(restaurant) %>% 
  ungroup() %>% 
  ggplot(aes(x = restaurant, y = total_fat)) +
  geom_col() +
  labs(x="Names of Restaurant", y="Total Fat", title="Data Visualisation 1", caption = "Image 1:Bar Graph")

#The three major attributes of bar graphs are:

#The bar graph helps to compare the different sets of data among different groups easily.
#It shows the relationship using two axes, in which the categories are on one axis and the discrete values are on the other axis.
#The graph shows the major changes in data over time.
```

#Add a variable to the dataset, which calculates the sum of cholesterol and sodium and call it `cholesterol_sodium`.Remove the variable `salad`
```{r}
cholestrol_sodium <- fastfood %>%
  group_by(restaurant) %>%
  summarise(cholestrol_sodium = sum(cholesterol, sodium)) %>%
  arrange(desc(cholestrol_sodium)) %>%
  ungroup()
kable(cholestrol_sodium)
fastfood %>%
  select(-(salad))
```

#Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 
```{r}
ggplot(fastfood, aes(sugar, protein, group = 1, colour = sugar)) +
  geom_point() +
  coord_flip()
```


